Hydra battles in Coq

### 2020-09-16 doc/chapter-ordinals.tex
minor modifications

\begin{Coqsrc}
Definition m_lt {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare}
            {B : Type}
  (m : B -> A) : relation B :=
  fun x y =>  on_lt (m x) (m y).

Lemma wf_measure  {A:Type}(lt: relation A)
            {compare : A -> A -> comparison}
            {on : ON lt compare}
            {B : Type}
            (m : B -> A) :
  well_founded (m_lt m). 
\end{Coqsrc}

@@

\subsection{A proof a termination using \texorpdfstring{$\omega^2$}{omega^2}}

Using the lemma of Sect.~\vref{sect:measure-ON}, we can define easily the function which merges two

@@

Require Import Coq.Program.Wf.

@@

  Program Fixpoint  merge  (ltb: A -> A -> bool)
          (xys: list A * list A)
          {wf (m_lt m) xys} :
    list A :=
    match xys with
      (nil, ys) => ys
    | (xs, nil) => xs
    | (x :: xs, y :: ys) =>
      if ltb x y then x :: merge  ltb (xs, (y :: ys))
      else y :: merge  ltb ((x :: xs), ys)
    end.

  Next Obligation.
    unfold m, m_lt; destruct xs; simpl; left; lia.
  Defined.

  Next Obligation.
    unfold m, m_lt ;cbn; destruct ys; simpl; right; lia.
  Defined.

End Merge.
\end{Coqsrc}

>>>>

\begin{Coqsrc}
Definition measure_lt {A:Type}{lt: relation A}
            {compare : A -> A -> comparison}
            {on : ON lt compare}
            {B : Type}
  (m : B -> A) : relation B :=
  fun x y =>  on_lt (m x) (m y).

Lemma wf_measure  {A:Type}(lt: relation A)
            {compare : A -> A -> comparison}
            {on : ON lt compare}
            {B : Type}
            (m : B -> A) :
  well_founded (measure_lt m). 
\end{Coqsrc}

@@

\subsection{A proof a termination using \texorpdfstring{$\omega^2$}{omega^2}} 
\label{sect:merge-example}.

Using the lemma of Sect.~\vref{sect:measure-ON}, we can define easily the function which merges two lists.

@@

Require Import Coq.Program.Wf List.
Require Import FunInd Recdef.

@@

  Function  merge  (ltb: A -> A -> bool)
          (xys: list A * list A)
          {wf (measure_lt m) xys} :
    list A :=
    match xys with
      (nil, ys) => ys
    | (xs, nil) => xs
    | (x :: xs, y :: ys) =>
      if ltb x y then x :: merge  ltb (xs, (y :: ys))
      else y :: merge  ltb ((x :: xs), ys)
    end.

  - intros.  unfold m, measure_lt;  cbn; destruct xs0; simpl; left; lia.
  - intros;    unfold m, measure_lt ;cbn; destruct ys0; simpl; right; lia.
   - auto.
  Defined.

End Merge.

Goal forall l,  merge nat Nat.leb (nil, l) = l.
  intro; now rewrite merge_equation.
Qed.
\end{Coqsrc}
